\textit{Supplementary materials for}: Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-20 paper/main.tex
added section on creating video trajectories and question embeddings, added table of top words from each topic to supplement

% supplemental tables
\newcommand{\questions}{S1}

@@

@@

\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A.
Building a document pool from sliding windows of text.} We decompose each
video's transcript into a series of overlapping sliding windows. The set of
transcript snippets (across all windows) may be treated as a set of
``documents'' for training a text embedding model. After training a text
embedding model using the two videos' sliding windows, along with the text from
each question in our pool (Tab.~\questions), } we construct ``trajectories''
through text embedding space by joining the embedding coordinates of successive
sliding windows from each video. \textbf{B. Embedding multiple videos and
questions.} Applying the same text embedding approach to each video, along with
the text of each question, results in one trajectory per video and one
embedding coordinate (dot) per question (blue: Four Fundamental Forces; green:
Birth of Stars; pink: general physics knowledge).}

@@

>>>>

% supplemental tables
\newcommand{\questions}{S1}
\newcommand{\topics}{S2}

@@

We extended an approach developed by~\citep{HeusEtal21} to construct text
embeddings for each moment of each lecture, and of each question in our pool.
Briefly, our approach uses a topic model~\citep{BleiEtal03}, trained on a set
of documents, to discover a set of $k$ ``topics'' or ``themes.'' Formally, each
topic is defined as a set of weights over each word in the model's vocabulary
(i.e., the union of all unique words, across all documents, excluding ``stop
words.''). Conceptually, each topic is intended to give larger weights to set
of words that appear conceptually related or that tend to co-occur in the same
documents. After fitting a topic model, each document in the training set, or
any \textit{new} document that contains at least some of the words in the
model's vocabulary, may be represented as a $k$-dimensional vector describing
how much the document (most probably) reflects each topic. (Unless, otherwise
noted, we used $k = 15$ topics.)

@@

\caption{\textbf{Constructing video content \textit{trajectories}. \textbf{A.
Building a document pool from sliding windows of text.} We decompose each
video's transcript into a series of overlapping sliding windows. The set of
transcript snippets (across all windows) may be treated as a set of
``documents'' for training a text embedding model. After training a text
embedding model using the two videos' sliding windows, along with the text from
each question in our pool (Tab.~\questions), } we construct ``trajectories''
through text embedding space by joining the embedding coordinates of successive
sliding windows from each video. \textbf{B. Embedding multiple videos and
questions.} Applying the same text embedding approach to each video, along with
the text of each question, results in one trajectory per video and one
embedding coordinate (dot) per question (blue: Four Fundamental Forces; green:
Birth of Stars; pink: general physics knowledge). Here we have projected the
15-dimensional embeddings into a 3D space using Uniform Manifold Approximation
and Projection~\citep[UMAP;][]{McInEtal18a}.}

@@

As illustrated in Figure~\ref{fig:sliding-windows}A, we start by building up a
corpus of documents using overlapping sliding windows that span each video's
transcript. Khan Academy videos are hosted on the YouTube platform, and all
YouTube videos are run through Google's speech-to-text API~\citep{HalpEtal16}
to derive a timestamped transcript of any detected speech in the video. The
resulting transcripts contain one timestamped row per line, and each line
generally corresponds to a few seconds of spoken content from the video. We
defined a sliding window length of (up to) $w = 30$ transcript lines, and we
assigned each window a timestamp according to the midpoint between its first
and last lines' timestamps. These sliding windows ramped up and down in length
at the very beginning and end of the transcript, respectively. In other words,
the first sliding window covered only the first line from the transcript; the
second sliding window covered the first two lines; and so on. This ensured that
each line of the transcript appeared in the same number ($w$) of sliding
windows. We treated the text from each sliding window as a single ``document,''
and we combined these documents across the two videos' windows to create a single
training corpus for the topic model.  The top words from each of the 15 discovered
topics may be found in Table~\topics.

After fitting a topic model to each videos' transcripts, we could use the
trained model to transform arbitrary (potentially new) documents into
$k$-dimensional topic vectors. A convenient property of these topic vectors is
that documents that reflect similar blends of topics (i.e., documents that
reflect similar themes, according to the model) will yield similar (in terms of
Euclidean distance, correlation, etc.) topic vectors. In general, the
similarity between different documents' topic vectors may be used to
characterize the similarity in content between the documents.

We transformed each sliding window's text into a topic vector, and then used
linear interpolation (independently for each topic dimension) to resample the
resulting timeseries to once per second. This yielded a single topic vector for
each second of each video. We also used the fitted model to obtain topic
vectors for each question in our pool (Tab.~\questions). Taken together, we
obtained a \textit{trajectory} for each video, describing its path through
topic space, and a single coordinate for each question
(Fig.~\ref{fig:sliding-windows}B). Embedding both videos and all of the
questions using a common model enables us to compare the content from different
moments of videos, compare the content across videos, and estimate potential
associations between specific questions and specific moments of video.

### 2023-01-20 paper/supplement.tex
added section on creating video trajectories and question embeddings, added table of top words from each topic to supplement

    31    &      GK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest? &                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electrom, atom \\\hline

@@

>>>>

    31    &      GK &                                                                                                                                                                                                   Which of the following lists of particles is ordered from smallest to largest? &                                                                                                       Electron, proton, nucleus, atom &                                                                       Atom, electron, proton, nucleus &                                                                                           Electron, nucleus, atom, neutron &                                                                                                  Neutron, nucleus, electron, atom \\\hline

@@

\newpage

\begin{table}[tp]
    \centering
\begin{tiny}
\begin{tabular}{r|l|l|l|l|l|l|l|l|l|l}

    \textbf{Topic} &       \textbf{1}  &        \textbf{2}  &               \textbf{3}  &           \textbf{4}  &       \textbf{5}  &        \textbf{6}  &             \textbf{7}  &           \textbf{8}  &        \textbf{9}  &               \textbf{10} \\\hline    
    0     &     star &    helium &             main &         mass &   atomic &  sequence &            get &       energy &      fuse &         hydrogen \\\hline
    1     &   charge &     force &             mass &      gravity &   strong &   attract &          large &     strength &  distance &  electromagnetic \\\hline
    2     &     huge &     force &  electromagnetic &        macro &      way &     scale &  concentration &        apply &      kind &           charge \\\hline
    3     &     atom &     dense &               go &     hydrogen &     slow &       get &           huge &     condense &      mass &            would \\\hline
    4     &   fusion &       get &        threshold &         core &    occur &      mass &      something &        start &   several &          jupiter \\\hline
    5     &   enough &  ignition &           proton &        force &      get &     close &        nucleus &      coulomb &    fusion &            would \\\hline
    6     &   energy &  pressure &         ignition &         mass &   little &      keep &        provide &       fusion &       get &         hydrogen \\\hline
    7     &   proton &      weak &          neutron &  interaction &      one &        go &        nucleon &       cesium &     extra &              get \\\hline
    8     &      run &      kind &              say &           go &     want &     would &            get &         well &      give &         although \\\hline
    9     &     huge &     cloud &            space &        float &  imagine &  hydrogen &           atom &          say &  distance &          combine \\\hline
    10    &      one &  hydrogen &           helium &           go &   proton &   neutron &           keep &       atomic &    detail &             fuse \\\hline
    11    &  gravity &     force &             weak &  interaction &    apply &  strength &       distance &          ten &  relative &             next \\\hline
    12    &    force &        go &    electrostatic &         call &   charge &    magnet &           side &      coulomb &      know &        different \\\hline
    13    &    force &      atom &          nucleus &     electron &     much &  hydrogen &            get &       around &   coulomb &           charge \\\hline
    14    &    force &     scale &          gravity &        start &     weak &     orbit &           keep &  fundamental &    around &         surprise \\

    \label{tab:topics}

\end{tabular}
\end{tiny}
\caption{\textbf{Topics.} The table displays the 10 top-weighted word from
    each of the 15 topics identified from sliding windows of two course video
    transcripts (see \textit{Constructing text embeddings of multiple videos
    and questions}).}
\end{table}
